DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-06 paper/comparison.tex
figure 12 revision

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/compare_core}
  \caption{Inferencing time across platforms based on number of cores 
used.}
  \label{fig:sys_core}
\end{figure}

Figure~\ref{fig:sys_core} shows the average control loop completion
timing as a function of the number of CPU cores on each of the four
system configurations. First, Tegra TX2 and the Intel UP exhibit
superio performance  compared with the Raspberry Pi 3 in 
all experiments. On average, the Intel UP is able to perform
inferencing operations more than twice as fast as the Raspberry Pi
3. The  difference is even greater with the TX2 as the performance is
about 3X faster using only the CPU and 10X faster when using the GPU.
As a result, they were all able to satisfy the 50 ms 
WCET by a very clear margin (in the worst case, the UP Board would 
still meet it by $\sim$20 ms), and, thus, demonstrates that they are 
more capable of autonomous driving than the Raspberry Pi 3.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/compare_core}
  \caption{Average control loop execution time.} 
  \label{fig:sys_core}
\end{figure}

Figure~\ref{fig:sys_core} shows the average control loop completion
timing of the four system configurations we tested as a function of
the number of CPU cores used.
First, both the Intel UP and Tegra TX2 exhibit superior performance
compared with the Raspberry Pi 3. 
When all four CPU cores are used, the Intel UP is 2.53X faster than
the Pi 3, while TX (CPU) and TX (GPU) are 3.6X and 7.6X times faster,
respectively, than the Pi 3. 
As a result, they are all able to satisfy the 50 ms 
WCET by a clear margin
%%  (in the worst case, the UP Board would 
%% still meet it by $\sim$20 ms) --> where's the data showing this?
, and, in case of TX2, 50 Hz or even 100 Hz real-time control is
feasible with the help of its GPU.
